DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-02-07 paper/comparison.tex

Figure~\ref{fig:sys_bench} shows the results. As discussed in 
Section~\ref{sec:eval-memhog}, we observed dramatic execution time
increases, up to 11.5X, in Raspberry Pi 3 as we increased the number of
co-scheduled tasks. We also observe increased control loop execution
timing in the Intel Up and Jetson TX2, but the degree of the increase is 
not as dramatic as the Pi 3. Compared to their respective solo timings 
(i.e., the model runs on a single core in isolation), Intel UP suffers up to
2.3X execution time increase; TX2 (CPU) and TX2 (GPU) suffer up to
2.2X and 2.1X increases, respectively. This is somewhat surprising
because the Raspberry Pi 3's cores are in-order architecture based while
the cores in the Intel Up and NVIDIA TX2 are out-of-order architecture
based, and that the memory intensive tasks on out-of-order cores can
generate more memory traffic. We believe that this is because the
memory subsystems in the Intel UP and TX2 platforms provide higher
performance than the memory subsystem of the Pi 3 as suggested from
the measured memory bandwidth results in Table~\ref{tbl:platforms}
('Measured Bandwidth').

>>>>

Figure~\ref{fig:sys_bench} shows the results. As discussed in 
Section~\ref{sec:eval-memhog}, we observed dramatic execution time
increases, up to 11.6X, in Raspberry Pi 3 as we increased the number of
co-scheduled tasks. We also observe increased control loop execution
timing in the Intel Up and Jetson TX2, but the degree of the increase is 
not as dramatic as the Pi 3. Compared to their respective solo timings 
(i.e., the model runs on a single core in isolation), Intel UP suffers up to
2.3X execution time increase; TX2 (CPU) and TX2 (GPU) suffer up to
2.2X and 2.1X increases, respectively. This is somewhat surprising
because the Raspberry Pi 3's cores are in-order architecture based while
the cores in the Intel Up and NVIDIA TX2 are out-of-order architecture
based, and that the memory intensive tasks on out-of-order cores can
generate more memory traffic. We believe that this is because the
memory subsystems in the Intel UP and TX2 platforms provide higher
performance than the memory subsystem of the Pi 3 as suggested from
the measured memory bandwidth results in Table~\ref{tbl:platforms}
('Measured Bandwidth').

### 2018-02-07 paper/intro.tex
8 -> 9 layers.

% DeepPicar introduction
In this paper, we present DeepPicar, a low-cost autonomous car
platform for research. From a hardware perspective,
DeepPicar is comprised of a Raspberry Pi 3 Model B quad-core
computer, a web camera and a RC car, all of which are affordable
components (less than \$100 in total).
The DeepPicar, however, employs state-of-the-art AI
technologies, including a vision-based end-to-end control system that
utilizes a deep convolutional neural network (CNN).
The network receives an image frame from a single forward
looking camera as input and generates a predicted steering angle
value as output at each control period in \emph{real-time}.
The network has 8 layers, about 27 million connections
and 250 thousand parameters (weights).
The network architecture is almost identical to that of NVIDIA's DAVE-2
self-driving car~\cite{Bojarski2016}, which uses a much more powerful
computer (Drive PX computer~\cite{drivepx}) than a Raspberry Pi~3.
We chose to use a Pi 3 not only because it is affordable, but also because it is representative
of today's mainstream low-end embedded multicore platforms found in
smartphones and other embedded devices.

@@

% all platforms have enough capacity to consolidate
Third, contention in shared hardware resources remains an important
issue when consolidating multiple workloads. 
In particular, we find that DNN inferencing is highly sensitive to
memory performance interference as we observe up to an 11.5X control
loop execution time increase, when memory performance intensive
applications are co-scheduled on idle CPU cores.
On the other hand, we find that DNN inferencing is not sensitive to
cache space.
%% ; we show that applying cache partitioning has negligible impact
%% in providing timing isolation on consolidated scenarios.
This finding
suggests that in order to guarantee real-time performance of DNN-based
control applications, solutions to guarantee their memory performance
are more important.

>>>>

% DeepPicar introduction
In this paper, we present DeepPicar, a low-cost autonomous car
platform for research. From a hardware perspective,
DeepPicar is comprised of a Raspberry Pi 3 Model B quad-core
computer, a web camera and a RC car, all of which are affordable
components (less than \$100 in total).
The DeepPicar, however, employs state-of-the-art AI
technologies, including a vision-based end-to-end control system that
utilizes a deep convolutional neural network (CNN).
The network receives an image frame from a single forward
looking camera as input and generates a predicted steering angle
value as output at each control period in \emph{real-time}.
The network has 9 layers, about 27 million connections
and 250 thousand parameters (weights).
The network architecture is almost identical to that of NVIDIA's DAVE-2
self-driving car~\cite{Bojarski2016}, which uses a much more powerful
computer (Drive PX computer~\cite{drivepx}) than a Raspberry Pi~3.
We chose to use a Pi 3 not only because it is affordable, but also because it is representative
of today's mainstream low-end embedded multicore platforms found in
smartphones and other embedded devices.

@@

% all platforms have enough capacity to consolidate
Third, contention in shared hardware resources remains an important
issue when consolidating multiple workloads. 
In particular, we find that DNN inferencing is highly sensitive to
memory performance interference as we observe up to an 11.6X control
loop execution time increase, when memory performance intensive
applications are co-scheduled on idle CPU cores.
On the other hand, we find that DNN inferencing is not sensitive to
cache space.
%% ; we show that applying cache partitioning has negligible impact
%% in providing timing isolation on consolidated scenarios.
This finding
suggests that in order to guarantee real-time performance of DNN-based
control applications, solutions to guarantee their memory performance
are more important.
